\documentclass{beamer}

% Set the theme and color scheme
\usetheme{metropolis}
\usecolortheme{default}

\title{Achievo: A Productivity Boosting Application}
\author{}
\date{}

\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}{Introduction}
    \begin{itemize}
        \item A user-centric web application for productivity.
        \item Addresses procrastination, lack of focus, and planning issues.
    \end{itemize}
\end{frame}

\begin{frame}{Objective}
    \begin{itemize}
        \item To build an app that gamifies productivity.
        \item To provide effective methods to improve focus and motivation.
    \end{itemize}
\end{frame}

\begin{frame}{Approach}
    \begin{itemize}
        \item User-centric development approach.
        \item Utilising multiple tried and tested techniques like Eisenhower Matrix, pomodoro, 1-3-5 rule, hour rule, milestone setter, fill the container, motivating spinning wheel, the good scroll, leaderboard, and group marathons.
    \end{itemize}
\end{frame}

\begin{frame}{Tech Stack}
    \begin{itemize}
        \item Front-end: HTML5, CSS3, JavaScript (React.js)
        \item Back-end: Node.js, Express.js, MongoDB
        \item Integration: RESTful APIs, Google Calendar API
    \end{itemize}
\end{frame}

\begin{frame}{Challenges and Learnings}
    \textbf{Challenges}
    \begin{enumerate}
        \item Finding it hard to implement what we learnt and taking excess time to figure stuff out.
        \item Lacking in time management.
        \item Implementation of ideas was harder than imagined.
    \end{enumerate}
    \textbf{Learnings}
    \begin{enumerate}
        \item Team and project management.
        \item Making a website using frontend UI and UX.
        \item Breaking things down into smaller parts makes implementation easy.
    \end{enumerate}
\end{frame}

\begin{frame}{Future Scope}
    \begin{enumerate}
        \item Complete the UI/UX according to the theme decided, improve responsiveness and animation.
        \item Build the remaining features.
        \item Finalise the logo.
        \item Learn and understand backend and API functioning.
        \item Work on deployment.
    \end{enumerate}
\end{frame}

\begin{frame}{Conclusion}
    Thank you for your attention. With Achievo, we aim to provide a comprehensive productivity application that helps users stay focused, motivated, and achieve their goals effectively.
\end{frame}

\end{document}
